---
output: github_document
---

# Reproduce Experiments 

To perform the experiments on a cluster, we used the package `bachtools`. The respective scripts are based on a submission to a Linux cluster with [Slurm](https://slurm.schedmd.com/documentation.html) as workload manager. 

Computing Infrastructure  | Linux Cluster |
--- | --- | 
Architecture | 28-way Haswell-EP nodes
Cores per Node | 1
Memory limit (per core) | 2.2 GB  


## Experiments on a Synthetic Function (Section 6.1)

To reproduce the experiments on a synthetic function, you simply run a couple of scripts. 

1. Create an experimental registry, add experiments and problem via sourcing the `generate_data.R`. 

```{r}
source("benchmarks/synthetic/generate_data.R")
```

The above script create an experimental registry in `regs/synthetic_tree_splitting`. 

The core part, which is the actual definition of the experiment is in the function `perform_tree_splitting_synthetic()` in the file `benchmarks/synthetic/config.R`.

2. Submit all your experiments 

```{r}
reg = loadRegistry("regs/synthetic_tree_splitting", writeable = TRUE)

# Overview table over experiments to be run
tab = summarizeExperiments(
  by = c("job.id", "algorithm", "problem", "lambda", "objective", "n.splits"))

# Submit all experiments to your local system  
submitJobs(tab)

# Alternatively, submit them to the linux cluster with respective resources
# source("benchmarks/resources.R")
submitJobs(tab, resources = resources.serial.default)
```

3. Reduce the results and store them in a compact format

Running the function `reduce_results_synthetic()` will store all results, splitted w.r.t. the problem and a specified directory. 


```{r}
reg = loadRegistry("regs/synthetic_tree_splitting")

# Check status of the experiments 
getStatus()

source("benchmarks/synthetic/reduce.R")
reduce_results_synthetic(reg, savedir = "data/runs/synthetic")
 ```


